### 2019-04-15 paper/paper.tex

@@

[NEEDS MORE DATA]

\subsubsection{Identifying Top Packages}
[NEEDS MORE DATA]

\subsubsection{Popular Package Dynamics}
[NEEDS MORE DATA]

>>>>

With the differences and changes in the relationships between
popularity measures explored, we can now focus on \code{npm}
rankings in particular, as it is most representative of the 
importance of a package to the \code{npm} ecosystem as a whole.
To obtain \code{npm} ranks over time, we first begin with the
complete dependency graph as of April 2019. We then examine
the date references on the edges of the graph to produce \code{PageRanks}
for each and every package on a monthly basis for the period of October 2010
to April 2019. From the list of \code{PageRanks} in each month, we then
produce the relative rank for every package present in the \code{npm}
ecosystem at that time.

\subsubsection{Identifying Top Packages}

One of the most obvious things to investigate is which packages
have historically performed best throughout the entirety of 
\code{npm}'s existence. To determine overall package popularity,
we use the geometric mean \code{npm} rank of a package over the full 
window of analysis, and order them from lowest to highest (i.e,
highly ranked to lowly ranked). Geometric mean is used in this instance
instead of arithmetic mean in order to limit the effect of outliers \cite{Wittern:2016}.
With popularity calculated in this manner, Figure \ref{topFive} presents 
the top five \code{npm} packages of all time.

The first thing to notice about these five packages is that the rankings
have changed since the time of the original paper. Gone are the packages
\code{uglify-js} and \code{coffee-script}, and newcomers \code{tape} and \code{mkdirp}
have appeared. Additionally, though the package \code{should} remains on the list,
it has fallen from the \#2 to the \#4 position.

Four of the five current champions are testing utilities---\code{mkdirp} is the sole exception, instead providing the ability to dynamically
create directories from within \code{node.js}. Curiously, the testing packages
are essentially all direct competitors of one another, providing a powerful 
demonstration of both the widespread importance of testing utilities as well as
the ability for the \code{npm} software ecosystem to support multiple core packages with
similar yet distinct functionality.

While these packages represent the most consistently popular
members of \code{npm}, we also evaluate the most popular packages
on a yearly basis. Figure \ref{ranksByYear} presents the top five packages
for each individual year from 2011 to 2019. As noted in the original paper,
the top packages per year are relatively stable from 2013 on \cite{Wittern:2016}.
One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
a tool for improving the quality of \code{JavaScript} code\footnote{https://www.npmjs.com/package/eslint}.

\subsubsection{Popular Package Dynamics}

@@

To better understand the evolution of package popularity,
we investigate the dynamics of the top rankings over time.
While figure \ref{ranksByYear} demonstrate that package popularity
appears to be relatively stable, we can examine the number of packages
entering (and therefore exiting) the top \code{n} packages per year in
order to obtain a better view of the ecosystem as a whole.
Table \ref{numEnteringTop} depicts amount of newcomers to the top
\code{npm} ranks each year, further supporting the observation that
core \code{npm} package popularity is becoming more stable as the 
ecosystem matures.
